\Title

### 2023-02-07 Grimaldi-etal-BiolCybernetics.tex

Let's formalize a layer of spiking neurons with heterogeneous delays (HD-SNN). Each neuron $\postsynaddr \in \postsynaddrspace$ connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses. Each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. Scanning all neurons $\postsynaddr$, we thus define the full set of $\Nsyn$ synapses, 
as  $\synapse = \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn)\}_{\ranksyn \in [1,\Nsyn]}$, where each synapse is associated to a presynaptic address $\presynaddr_\ranksyn$, a postsynaptic address $\postsynaddr_\ranksyn$, a weight $\synapticweight_\ranksyn$, and a delay $\synapticdelay_\ranksyn$. This defines the full connectivity of the HD-SNN model. Of interest is to define the receptive field of a postsynaptic neuron $\synapse^\postsynaddr =  \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn) \| \postsynaddr_\ranksyn=\postsynaddr\}_{\ranksyn \in [1,\Nsyn]} $, or the emitting field of a presynaptic neuron $\synapse_\presynaddr =  \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn) \| \presynaddr_\ranksyn=\presynaddr\}_{\ranksyn \in [1,\Nsyn]}$. As a consequence, a postsynaptic neuron $\postsynaddr$ receives, on its receptive field, an event stream which is multiplexed by the synapses into a new event stream defined by the union of the sets generated by each emitting field from the presynaptic space: 
$ \cup_{\arank \in [1,\numevent]} \{ \{(\postsynaddr_\ranksyn, \synapticweight_\ranksyn, \timev_\arank + \synapticdelay_\ranksyn) \}_{ \ranksyn \in \synapse_{\presynaddr_\arank}} \}$. This new stream of events is by nature ordered in time as events reach the soma of post-synaptic neurons. In particular, when post-synaptic neurons are activated on their soma by this spatio-temporal motif, the discharge probability will increase, notably when these spikes converge on the soma in a synchronous manner.

>>>>

Let's formalize a layer of spiking neurons with heterogeneous delays (HD-SNN). Each neuron $\postsynaddr \in \postsynaddrspace$ connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses. Each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. Scanning all neurons $\postsynaddr$, we thus define the full set of $\Nsyn$ synapses, 
as  $\synapse = \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn)\}_{\ranksyn \in [1,\Nsyn]}$, where each synapse is associated to a presynaptic address $\presynaddr_\ranksyn$, a postsynaptic address $\postsynaddr_\ranksyn$, a weight $\synapticweight_\ranksyn$, and a delay $\synapticdelay_\ranksyn$. This defines the full connectivity of the HD-SNN model. Of interest is to define the receptive field of a postsynaptic neuron $\synapse^\postsynaddr =  \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn) \| \postsynaddr_\ranksyn=\postsynaddr\}_{\ranksyn \in [1,\Nsyn]} $, or the emitting field of a presynaptic neuron $\synapse_\presynaddr =  \{(\presynaddr_\ranksyn, \postsynaddr_\ranksyn, \synapticweight_\ranksyn, \synapticdelay_\ranksyn) \| \presynaddr_\ranksyn=\presynaddr\}_{\ranksyn \in [1,\Nsyn]}$. As a consequence, a postsynaptic neuron $\postsynaddr$ receives an event stream which is multiplexed by the synapses of its receptive field. It results in a weighted event stream: 
$\event_\postsynaddr = \{(\presynaddr_\arank, \timev_\arank+\synapticdelay_\ranksyn) \| \presynaddr_\arank = \presynaddr_\ranksyn \}_{\arank \in [1,\numevent], \ranksyn \in \synapse^\postsynaddr}$. Unlike the binary stream of events as input, once integrated by the synapses, the postsynaptic neurons receives a weighted stream of event such that for each event $\arank$ its value is $\synapticweight_\arank$. This new stream of events is by nature ordered in time as events reach the soma of post-synaptic neurons. In particular, when post-synaptic neurons are activated on their soma by this spatio-temporal motif, the discharge probability will increase, notably when these spikes converge on the soma in a synchronous manner.
